\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{utopia}
\usepackage{ulem}
\usepackage{contour}
\usepackage[pdftex, colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{fancyhdr}
\usepackage{color,soul}
\definecolor{lightblue}{rgb}{0.957,.941,0.837}
\definecolor{lightyellow}{rgb}{1.0, 0.98, 0.8}
\definecolor{mygray}{gray}{0.4}
\sethlcolor{lightyellow}


% underline decorations
\renewcommand{\ULdepth}{2.2pt}
\contourlength{0.8pt}

\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\baselinestretch}{1}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\normalsize{
    \textbf{#1}{#2}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #4} \\
      \text{\normalsize#3} & {\small \textit{#2}}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Large{DANISH PRAKASH}} \\
    \href{https://danishprakash.github.io/}{{danishprakash.com}}  \href{mailto:danishprakash@outlook.com}{{ ¥  {danishprakash@outlook.com}}} \\
    \text{{+91 9821371321}} & \text{{New Delhi, India}}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amity University}{Noida, India}
      {Bachelor of Technology in Computer Science;  CGPA: 7.27}{August 2014 - November 2018}\vspace{0.3em}
    \resumeSubheading
      {Bal Bharati Public School}{ Delhi, India}
      {Class XII\textsuperscript{th} CBSE Board, Science;  86\%}{April 2012 - May 2014}\vspace{0.3em}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \renewcommand{\baselinestretch}{0.5}
 
    \resumeSubheading
      {DataGrokr} {Delhi, India}
      {Software Engineering Intern}{November 2018 - Present}
      \resumeItemListStart
        \setspac
        \resumeItem{}
        {Implemented CSV export functionality onto a ReactJS based web application.}
      \resumeItemListEnd 

      \resumeSubheading
      {SocialCops} {Delhi, India}
      {Software Engineering Intern}{February 2018 - May 2018}
      \resumeItemListStart
        \setspac
        \resumeItem{}
        {Rewrote a Python application used for retrieving funnel data from the database and turned it into a package.}
        \resumeItem{}
        {Increased user retention on web platform by implementing search filters by tags and names.}
        \resumeItem{}
        {Developed an Alexa skill which responds to funnel based queries using real-time data hosted from AWS Lambda.}\vspace{0.3em}
      \resumeItemListEnd
    
    \resumeSubheading
      {AT\&T}{Noida, India}
      {Software Development Intern}{May 2017 - June 2017}
      \resumeItemListStart
        \resumeItem{}
          {Developed a functional command-line interpretor(shell) in C for Unix based 
          systems.}
        \resumeItem{}
          {Feature set includes piping commands, history recollection, \& colored output.}\vspace{0.3em}
      \resumeItemListEnd

    \resumeSubheading
      {Sportido}{Noida, India}
      {UX Designer}{July 2016 - February 2017}
      \resumeItemListStart
         \resumeItem{}
         {Illustrated UI wireframes for the iOS application.}
        \resumeItem{}
          {Redesigned the UI for the android application as per material guidelines.}\vspace{0.3em}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
      \resumeSubItem{{\textbf{pysplice}}}
      {: A Python interface to splice(2) system call written in C.}
    \resumeSubItem{\href{https://github.com/danishprakash/vim-zen}{{\textbf{vim-zen}}}}
      {: Minimalistic Vim plugin manager with multithreading written in Vimscript and Python.}
      \resumeSubItem{\href{https://github.com/danishprakash/vim-githubinator}{{\textbf{vim-githubinator}}}}
      {: Vim plugin to show selected text on Github remote written in Vimscript.}
    \resumeSubItem{\href{https://github.com/danishprakash/goodreadsh}{{\textbf{goodreadsh}}}}
      {: Command line interface for Goodreads.com written in Bash.}
        \resumeSubItem{\href{https://github.com/danishprakash/githubfs}{{\textbf{GithubFS}}}}
      {: Read only virtual filesystem for Github using FUSE written in Python.}
    \resumeSubItem{\href{https://github.com/danishprakash/amizone-cli}{{\textbf{amizone-cli}}}}
      {: CLI for college portal for checking class schedules, courses \& more written in Python.}
     
  \resumeSubHeadingListEnd
  
 \section{Skills}
    \resumeSubHeadingListStart
        \resumeSubItem{Language}
            {:    Python, C/C++, JavaScript, Vimscript, Bash , Django, Flask, ReactJS}
        \resumeSubItem{Tools}
            {:    Git, MongoDB, GDB, GCC, Vim}
            
    \resumeSubHeadingListEnd

\section{OSS Contributions}
    \resumeSubHeadingListStart
    
        \resumeSubItem{Google Code-In 2017}
        { - Mentor}
      
        \resumeSubItem{Contributor}
        { - GNOME, Coala, CPython, Neovim}

    \resumeSubHeadingListEnd

\section{Volunteering}
  \resumeSubHeadingListStart
        \resumeSubItem{Child Rights \& You (CRY)}
        {: Designer (North Delhi Team)}
        
    \resumeSubHeadingListEnd
    
% \section{Extra Curricular}
%     \resumeSubHeadingListStart
%         \resumeSubItem{}
%         {Sport programming, badminton and reading.}
    
%     \resumeSubHeadingListEnd
    
\section{Extra}
    \resumeSubHeadingListStart
        \resumeSubItem{Languages}
        {: English, Hindi, German}
            
        \resumeSubItem{Links}
        {:    
        \href{https://github.com/danishprakash}{Github}, 
        \href{https://www.linkedin.com/in/danishprakash/}{LinkedIn}}\vspace{1em}
        
    \resumeSubHeadingListEnd
    
    
\lfoot{\scriptsize{\textcolor{mygray}{updated - 2018/11/17}}}

\end{document}
